---
title: "Network-Analysis-Project"
author: "Group-5 Anshita Aishwarya, Shrutika Swamy"
date: "12/15/2021"
output: pdf_document
---

## Importing the required libraries

```{r}
library(stringr)
library(sjmisc)
library(igraph)
library(dplyr)
library(ggplot2)
```

## Data Cleaning

```{r}

# Data Load
Keyword_data <- read.csv('Keyword_data.csv')

# Removing the 1st column "Title"
Keyword_data <- Keyword_data[-1]

# Dropping the rows that have null entries
Keyword_data <- Keyword_data[!apply(Keyword_data == "", 1, all), ]
rownames(Keyword_data) <- 1:49

```

## Creating a Keyword Adjacency Matrix
An adjacency matrix is a square matrix used to denote the weights between N x N items. In practice, it is used to map the association between graph nodes.

```{r Task 1.1}

options(warn = -1)

# Obtaining all the unique keywords from the dataset
keywords <- unique(c(Keyword_data$Keyword.1, Keyword_data$Keyword.2, Keyword_data$Keyword.3,
                   Keyword_data$Keyword.4, Keyword_data$Keyword.5, Keyword_data$Keyword.6,
                   Keyword_data$Keyword.7, Keyword_data$Keyword.8, Keyword_data$Keyword.9,
                   Keyword_data$Keyword.10, Keyword_data$Keyword.11, Keyword_data$Keyword.12))
keywords <- keywords[!keywords == ""]

# Concatenate all the keywords in each row to a single string
# Matrix to store the concatenated keywords (Keyword.1, Keyword.2 and so on) for each row
KCN_each_row <- matrix(data = "|", nrow = 49, ncol = 1)

# for loop to iterate through the 49 rows to obtain concatenated strings for each row
# Adding a pipe delimiter between keywords so that it checks for the exact string while matching for creating adjacency matrix
for(i in 1 : nrow(KCN_each_row)) {
  for(j in 1 : ncol(Keyword_data)) {
    KCN_each_row[i,] <- paste(KCN_each_row[i,], Keyword_data[i,j], '|')
  }
}


# Creating a matrix to store the final weighted co-occurrence result
KCN_data <- matrix(data=0, nrow = length(keywords), ncol = length(keywords))
rownames(KCN_data) <- keywords
colnames(KCN_data) <- keywords

# Storing the colnames and rownames in variables to use it to iterate through the final matrix
keywords_rows <- rownames(KCN_data)
keywords_columns <- colnames(KCN_data)

for(i in 1 : nrow(KCN_data)) {
  for(j in 1 : ncol(KCN_data)) {
    
    # Create a matrix to count the co-occurrences of i-th and j-th keyword in each row of Keyword_data
    # Gets reset for each new column keyword of the KCN matrix
    count_each_keyword <- matrix(data = 0, nrow = length(KCN_each_row))
    for(k in 1 : length(KCN_each_row)) {
      
      keyword_to_check_row <- paste('|', keywords_rows[i], '|')
      keyword_to_check_column <- paste('|', keywords_columns[j], '|')
      count_each_keyword[k] <- as.integer((str_contains(KCN_each_row[k], keyword_to_check_row))
         && (str_contains(KCN_each_row[k], keyword_to_check_column)))
      
      # Setting the diagonal elements of the KCN Matrix as O
      if(i == j)
        KCN_data[i,j] <- 0
      else
        # Setting the total occurrence values for each keyword pair
        KCN_data[i,j] <- colSums(count_each_keyword)
    }
  }
}

sum(KCN_data)
View(KCN_data)

```

## Creating a weighted Network using Adjacency Matrix
A network is a connection of interacting nodes using edges. When the edges represent the number of connections, then the network is called a weighted network. 

```{r Task 1.2}

# Creating the weighted network
KCN_network <- graph_from_adjacency_matrix(KCN_data, mode = "undirected", weighted = TRUE)
summary(KCN_network)

# Exploring the igraph data
# number of edges
gsize(KCN_network)
# number of vertex
gorder(KCN_network)
# node list
V(KCN_network)
# edge list
E(KCN_network)

KCN_plot <- igraph::simplify(KCN_network, remove.multiple = TRUE, remove.loops = TRUE)
plot(KCN_plot,
     layout = layout_with_graphopt,
     edge.arrow.size = 0.1,
     vertex.size = 3,
     vertex.color = "red",
     vertex.label.cex = 0.5)
title(main = list("Rarely Used Routes", cex=1.5))

```

## Determing the Node Degree and Strength of each Node

```{r Task 1.3}

KCN_degree_strength <- cbind(degree(KCN_network, mode = "all"), strength(KCN_network, mode = "all"))
KCN_degree_strength <- as.data.frame(KCN_degree_strength)
colnames(KCN_degree_strength) <- c("Degree", "Strength")

# View(KCN_degree_strength)

```

## Finding:
1.) Top 10 Nodes by Degree
2.) Top 10 Nodes by Strength
3.) Top 10 Node Pairs by Weight

```{r Task 1.4}

# Top 10 Nodes by Degree
KCN_degree_top10 <- KCN_degree_strength %>%
  select(Degree) %>%
  arrange(desc(Degree)) %>%
  top_n(10)

# Top 10 Nodes by Strength
KCN_strength_top10 <- KCN_degree_strength %>%
  select(Strength) %>%
  arrange(desc(Strength)) %>%
  top_n(10)

# Top 10 Node Pairs by Weight
KCN_node_pairs <- as.data.frame(E(KCN_network)$weight)
edges <- as.data.frame(as_edgelist(KCN_network, names = TRUE))
edges <- as.data.frame(paste(edges$V1, edges$V2, sep = " -- "))
KCN_node_pairs <- cbind(edges = edges, weight = KCN_node_pairs)
colnames(KCN_node_pairs) <- c("Node Pairs", "Weight")
KCN_node_pairs_top10 <- KCN_node_pairs %>%
  arrange(desc(Weight)) %>%
  slice(1:10)

# View(KCN_degree_top10)
# View(KCN_strength_top10)  
# View(KCN_node_pairs_top10)
```

## Plotting Average Strength v/s Degree of the Network

```{r Task 1.6}

#Calculating average strength for different degree values
KCN_avg_Strength_by_degree <- KCN_degree_strength %>%
  group_by(Degree) %>%
  summarise(Avg_Strength = mean(Strength))

#Average Strength v/s Degree
  ggplot(KCN_avg_Strength_by_degree, aes(Degree, Avg_Strength, size = Avg_Strength)) +
  geom_point(alpha = 0.5) +
  scale_size(name = "Avg Strength")+
  ggtitle("Average Strength v/s Degree of the Network Graph") +
  xlab("Degree of the network") +
  ylab("Average Strength of the network") +
  theme(plot.title = element_text(size = 13, face = "bold.italic", color = "red", hjust = 0.5),
        axis.title.x = element_text(size = 7, face = "bold", colour = "blue"),
        axis.title.y = element_text(size = 7, face = "bold", colour = "blue"),
        axis.text.x = element_text(size = 5, angle = 0),
        axis.text.y = element_text(size = 5, angle = 90),
        legend.position = "right",
        legend.title = element_text(size = 7, face = "bold"),
        legend.text = element_text(size = 7, face = "bold"),
        strip.text = element_text(size = 7))

```
